Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-10-20 draft.tex
update assumptions in prop 1 in draft

\begin{enumerate}
\item \textit{For both players $g$ and $s$, $Q_{it} \geq L_{it} \ \forall t$: in each period, remaining in the status quo is better than ceding.}

\item \emph{For both players $g$ and $s$, $\frac {Q_{it}}{1-\delta} \geq  -\zeta_i+\frac{W_{it}(p_1) + L_{it}(1-p_1)}{1-\delta} \ \forall n$: in each period, the expected outcome under war is worse than the status quo.}

\item \textit{$\alpha \geq \beta$: reunification is more important for the patron to avoid than for the international community to achieve.}

@@

\item  \textit{$B_{p1} \geq\frac{\beta}{1-\delta} - \left(q_{s1} - l_{s1} \right)$: the patron can afford to deter player $c$ from inducing reunification at the beginning of the game.}

>>>>

\begin{enumerate}
\item \textit{For both players $g$ and $s$, $Q_{i0} \geq L_{i0}$: remaining in the status quo is better than ceding at the beginning of the game.}

\item \emph{For both players $g$ and $s$, $\frac {Q_{i0}}{1-\delta} \geq  -\zeta_i+\frac{W_{i0}(p_1) + L_{i0}(1-p_1)}{1-\delta}$: the expected outcome under war is worse than the status quo at the beginning of the game.}

\item \textit{$\frac{\alpha}{1-\de} \geq \frac{\beta}{1-\de} + \mu$: reunification is more important for the patron to avoid than for the international community to achieve.}

@@

\item  \textit{$B_{p1} \geq\frac{\beta}{1-\delta} - \left(Q_{s0} -\mu - L_{s0} \right)$: the patron can afford to deter player $c$ from inducing reunification at the beginning of the game.}
